---
title: "p8105_hw1_yw3095"
author: "Yixuan Wang"
date: "9/21/2018"
output: github_document
---
```{r setup, include=FALSE}
getwd()
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

##problem 1:
This problem focuses on plotting and the use of inline R code.

First, we create a dataframe:
```{r df1}
set.seed(1234)
hw1_df = tibble(
  norm_samp = runif(10, min = 0, max = 5),
  vec_logical = norm_samp > 2,
  vec_char = c("one","two","three","four","five","six","seven","eight","nine","ten"),
  vec_factor = factor(c("male","female","male","male","male","female","female","male","female","male"))
)
```
examine classes
```{r examine_class}
class(hw1_df$vec_logical)
class(hw1_df$vec_char)
class(hw1_df$vec_factor)
```

Try to take the mean of each variable in your dataframe. 
```{r mean}
mean(hw1_df$norm_samp)
mean(hw1_df$vec_logical)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)
```

*   What works and what doesn’t? Why?
    *   **Answer**: The random sample and the logical vector work but the charcter vector and factor vector don't work as their classes are not numeric or logical.
    
Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r convert, results= 'hide'}
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_char)
as.numeric(hw1_df$vec_factor)
```

*   Explain what happened?
    *   **Answer**: The logical and factor vectors can be converted to numeric vector, but the charactor factor cannot be converted. 
    
Convert the character variable from character to factor to numeric; similarly, convert the factor variable from factor to character to numeric. 
```{r}
as.numeric(as.factor(hw1_df$vec_char))
as.numeric(as.character(hw1_df$vec_factor))
```
**Result**: The character variable can be converted from character to factor to numeric, but the factor variable cannot be converted from factor to character to numeric.

##problem 2:
This problem focuses on plotting and the use of inline R code.

First, we create a dataframe:
```{r df2}
plot_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logical = x + y > 0,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```
**Summary**:

*    The dataset "plot_df" is a `r nrow(plot_df)` by `r ncol(plot_df)` table. 
*    The mean of the x is `r mean(plot_df$x)`, and the median of the x is `r median(plot_df$x)`. 
*    The proportion of cases for which the logical vector is true is `r (sum(plot_df$vec_numeric)/1000*100)`%.

**Plots**:

*   Make a scatterplot of y vs x (color using the logical variable):
```{r plot_1}
plot_logi = ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_logical)) + geom_point()
plot_logi
```
*   Make a scatterplot of y vs x (color using the numeric variable):
```{r plot_2}
plot_num = ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_numeric)) + geom_point()
plot_num
```
*   Make a scatterplot of y vs x (color using the factor variable):
```{r plot_3}
plot_fac = ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_factor)) + geom_point()
plot_fac
```

*   Export the first scatterplot to my project directory 
```{r export_plot1}
ggsave("scatter_plot.pdf", plot_logi, height = 4, width = 6)
```