---
title: "p8105_hw1_yw3095"
author: "Yixuan Wang"
date: "9/21/2018"
output: github_document
---
```{r setup, include=FALSE}
getwd()
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
```

##problem 1:
This problem focuses on plotting and the use of inline R code.

First, we create a dataframe:
```{r}
set.seed(1234)
hw1_df = tibble(
  norm_samp = runif(10, min = 0, max = 5),
  vec_logical = c(FALSE,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE,FALSE,TRUE,TRUE),
  vec_char = c("good","bad", "good","good","good","bad","good","good","good","bad"),
  vec_factor = factor(c("one","two","three","four","five","six","seven","eight","nine","ten"))
)
```
examine classes
```{r}
class(hw1_df$vec_char)
class(hw1_df$vec_factor)
```
Try to take the mean of each variable in your dataframe. 
```{r}
mean(hw1_df$norm_samp)
mean(hw1_df$vec_logical)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)
```

*   What works and what doesn’t? Why?
    *   answer:The random sample and the logical vector work but the charcter vector and factor vector don't work as their classes are not numeric or logical.
    
Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r convert, results= 'hide'}
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_char)
as.numeric(hw1_df$vec_factor)
```

*   Explain what happened?
    *   answer:
    
Convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. 

##problem 2:
This problem focuses on plotting and the use of inline R code.

First, we create a dataframe:
```{r}
  x = rnorm(1000)
  y = rnorm(1000)
  vec_logical = x + y > 0
  
plot_df = tibble(
  x,
  y,
  vec_logical,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```
The size of the dataset is `r length(plot_df$x)`. The mean of the x is `r mean(plot_df$x)`, and the median of the x is `r median(plot_df$x)`. The proportion of cases for which the logical vector is true is `r percent(mean(plot_df$vec_numeric))`.

1.    Make a scatterplot of y vs x (color using the logical variable):
```{r}
ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_logical)) + geom_point()
```
2.    Make a scatterplot of y vs x (color using the numeric variable):
```{r}
ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_numeric)) + geom_point()
```
3.    Make a scatterplot of y vs x (color using the factor variable):
```{r}
ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_factor)) + geom_point()
```

*   Export the first scatterplot to my project directory 
```{r, fig.show = "hide"}
ggplot(plot_df, aes(x = x, y = y, color = plot_df$vec_logical)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
